\documentclass[10pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.72in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{multicol}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.2em}

% Editable layout controls
\newcommand{\NameSize}{\fontsize{21.5}{23.5}\selectfont}
\newcommand{\RoleSize}{\fontsize{11.3}{13}\selectfont}
\newcommand{\BodySize}{\fontsize{10.15}{13.1}\selectfont}
\newcommand{\HeaderGap}{0.28em}
\newcommand{\ContactTopGap}{0.28em}
\newcommand{\HeaderBottomGap}{0.55em}
\newcommand{\SectionGap}{0.58em}
\newcommand{\EntryGap}{0.26em}
\newcommand{\BulletGap}{0.12em}
\newcommand{\BulletTopGap}{0.14em}
\newcommand{\ContactGap}{0.28em}
\newcommand{\SkillsGap}{0.18em}
\newcommand{\LeftColumnWidth}{0.74\textwidth}
\newcommand{\RightColumnWidth}{0.23\textwidth}
\newcommand{\TitleInstitutionGap}{0.28em}

\definecolor{heading}{HTML}{1F2937}
\definecolor{textgray}{HTML}{4B5563}
\definecolor{lighttext}{HTML}{6B7280}
\definecolor{rulegray}{HTML}{D1D5DB}

\titleformat{\section}
  {\fontsize{11.5}{13}\selectfont\bfseries\color{heading}\scshape}
  {}
  {0pt}
  {}
  [\vspace{0.2em}\color{rulegray}\titlerule]

\titlespacing*{\section}{0pt}{0.8em}{0.32em}

\newcommand{\cvheader}[4]{
  {\centering
  {\NameSize\bfseries\color{heading} #1\par}
  \vspace{\HeaderGap}
  {\RoleSize\color{textgray} #2\par}
  \vspace{\ContactTopGap}
  {\footnotesize\color{lighttext} #3 \hspace{\ContactGap} #4\par}
  \vspace{\HeaderBottomGap}
  \par}
}

\newcommand{\sectionspace}{\vspace{\SectionGap}}

\newcommand{\cventry}[4]{
  \begin{tabularx}{\textwidth}{@{}p{\LeftColumnWidth}@{\hfill}p{\RightColumnWidth}@{}}
    {\bfseries\color{heading} #1} & {\RaggedLeft\small\color{lighttext} #2} \\[-\TitleInstitutionGap]
    {\itshape\color{textgray} #3} & \\
  \end{tabularx}
  \ifx&#4&%
  \else
    \vspace{\BulletTopGap}
    \begin{itemize}[itemsep=\BulletGap, topsep=0pt, parsep=0pt, partopsep=0pt]
      #4
    \end{itemize}
  \fi
  \vspace{\EntryGap}
}

\begin{document}
\BodySize
\setstretch{1.02}

\cvheader
  {Adriana Rup\'erez Arellano}
  {{\fontsize{14.2}{16}\selectfont Data Scientist and Engineer}}
  {Madrid, Spain (Open to remote work) \textbar\ +34 717 71 56 24 \textbar\ \href{mailto:adriana.rupereza@gmail.com}{adriana.rupereza@gmail.com}} 
  {\href{https://www.linkedin.com/in/adrianaruperezarellano}{LinkedIn} \hspace{\ContactGap} \href{https://github.com/adriana-ruperez}{GitHub}}


\section{Education}
\cventry
  {B.Sc. in Data Science and Engineering}
  {Sep. 2022 -- June 2026}
  {University Carlos III of Madrid | Madrid, Spain}
  {
    \item Current grade: 7.74/10.
    \item Pursuing UC3M's TFG Emprende (official Entrepreneurship Distinction) focused on innovation, entrepreneurship, and technology-driven final-year project development.
    \item Relevant coursework: Data Structures and Algorithms, Data Bases, Machine Learning I, II and Applications of Machine Learning.
    }

\cventry
  {International Mobility Program in Computer Science}
  {Sep. 2024 -- May 2025}
  {Case Western Reserve University | Cleveland, USA}
  {
    \item Relevant coursework: Deep Generative Models, Data Mining for Big Data, Robotics, Computational Perception, and Bayesian Analysis. GPA: 3.876/4.
  }

\cventry
  {Technological High School}
  {Sep. 2007 -- Jun. 2022}
  {School Miravalles-El Red\'in | Pamplona, Spain}
  {
    \item Final grade: 9.67/10. EVAU score: 13.401/14, among the highest grades in Navarre.
    \item Exchange year in Bayonne, France (2018--2019) and semester in Chicago, US (2016).
  }

\section{Experience}
\cventry
  {Software Architect and AI Integration Intern}
  {Jan. 2026 -- Jul. 2026}
  {Ericsson | Madrid, Spain}
  {
    \item Developed internal data migration tools for telecom systems, supporting \textbf{ETL workflows} for subscriber data using Java, Python, Pentaho Data Integration, shell scripting and CI/CD pipelines.
    \item \textbf{Created AI-powered agents} by building \textbf{domain-specific knowledge bases} and integrating \textbf{automation} into development, testing, and documentation workflows.
    \item Improved reliability of migration processes by \textbf{designing and executing functional tests}, regression suites, test datasets, and simulated environments to validate data accuracy and integrity.
  }

\cventry
  {Freelance Mobile and Cloud Developer}
  {Jan. 2026 -- Jun. 2026}
  {Milanes Transport | NEMT business in Florida, EEUU}
  {
    \item Designed and built the company's digital ecosystem for drivers and passengers, translating operational needs into internal and \textbf{customer-facing mobile products}.
    \item Developed and published an internal driver and a passenger \textbf{mobile application} to the iOS and Android stores, and deployed the supporting \textbf{cloud infrastructure and backend services}.
  }

\cventry
  {Data and Client Operations and Automation Support}
  {Jun. 2023 -- May 2026}
  {Practice C.V.M. | Family real estate business}
  {
    \item \textbf{Captured clients} through property portals, showed rooms, and \textbf{closed 20+ room rental contracts}.
    \item Built a \textbf{CRM and admin web platform} with React and Supabase for property, tenant, and contract management.
    \item \textbf{Automated} contract generation, expiration alerts, and document workflows, including a \textbf{local AI-assisted leasing process}.
  }

\cventry
  {Ski and Leisure Instructor}
  {Dec. 2019 -- Apr. 2024}
  {Club Pirineista Mayencos and Ski Club Noroeste | Spain}
  {
    \item Delivered \textbf{adaptive lessons} for different ages and skill levels, including beginners and students with \textbf{special needs}.
    \item \textbf{Led groups of up to 10 participants} and coordinated with other instructors in inclusive learning environments.
  }

\section{Projects and Leadership}
\cventry
  {Founder and Developer, CampusRide}
  {Ongoing}
  {Independent project}
  {
    \item \textbf{Founded and developed} a ridesharing mobile application for the UC3M community, building it \textbf{end-to-end} with Flutter, Firebase and \textbf{Google Cloud Platform}.
    \item \textbf{Built and coordinated} a small team of 4 to support ongoing product development, content creation, university relations, and day-to-day app operations, fostering \textbf{ownership and execution standards} across the project.
    \item Application available on \href{https://apps.apple.com/es/app/campusride/id6751732085}{iOS} and \href{https://play.google.com/store/apps/details?id=com.ara.campusride}{Android} stores and used by \textbf{almost 350 students}.
  }

\cventry
  {AI/ML Developer}
  {September 2025 -- January 2026}
  {Curricular project with Sandoz and Universidad Carlos III de Madrid}
  {
    \item \textbf{Built a RAG-based assistant} to turn a \textbf{large unstructured document base} into an internal query tool for employees.
    \item Worked on \textbf{ingestion, retrieval, topic-based routing, and OCR} in Python across \textbf{local and cloud-based setups}.
  }

\cventry
  {University Associations}
  {Sep. 2024 -- May 2026}
  {Open UC3M (UC3M) and Coding Club (CWRU)}
  {
    \item \textbf{Full Stack Developer}, Open UC3M (Sep. 2025 -- May 2026): contributed to a university social network mobile application using React Native, Django, and Render.
    \item \textbf{Member, Coding Club} (Sep. 2024 -- Apr. 2025): participated in the development of a university marketplace app using React Native and Supabase.
  }

\vspace{0.6em}
\noindent \textbf{Other relevant projects in GitHub}
\vspace{0.4em}
\begin{itemize}[itemsep=\BulletGap, topsep=0pt, parsep=0pt, partopsep=0pt]
  \item \textbf{Encoder-decoder architecture} for automatic radiology report generation from chest X-ray images, NEMT Android mobile app.
\end{itemize}
  
\section{Technical Skills}
\vspace{0.3em}
\textbf{Backend \& Frontend:} Python, TypeScript, FastAPI, Django, Node.js, React Native, Flutter/Dart, HTML, CSS

\vspace{\SkillsGap}
\textbf{AI \& Data Science:} Agentic AI, RAG, NLP, LLMs, OCR, PyTorch, TensorFlow, Transformers, Scikit-learn, RStan

\vspace{\SkillsGap}
\textbf{Data Engineering \& Databases:} SQL, NoSQL, MongoDB, Supabase, Firebase, Pentaho PDI

\vspace{\SkillsGap}
\textbf{Cloud, DevOps \& Tools:} Docker, GitHub/GitLab CI/CD, Google Cloud Platform, Azure, Render, Jupyter, n8n
\section{Languages}
\vspace{0.3em}
\textbf{Spanish:} Native \hfill \textbf{English:} Full professional proficiency (C1) \hfill \textbf{French:} Full professional proficiency (C1)

\section{Certifications}
\vspace{-0.8em}
\begin{multicols}{2}
\begin{itemize}[itemsep=\BulletGap, topsep=0em, parsep=0pt, partopsep=0pt]
  \item CAE C1 Advanced (Cambridge University)
  \item DALF C1 (France Éducation International)
  \item Level 1 Sports Technician (Tandem)
  \item Dipl\^ome National du Brevet (Ministère de l’Éducation Nationale Française)
\end{itemize}
\end{multicols}

\end{document}
